### 2013-04-08 drafts/general_writeup/writeup.tex
Added brief description of holes to general writeup.

>>>>

\section{Holes}
In real-world applications, many of the useful degrees of freedom are
continuous, and it would be useful to have parameters that could be
fit in a systematic way. Doing this requires a small extension to the
framework presented so far: we add a special type of construct as a
primitive of the language. We call these holes. Each hole is a
placeholder for values of a specific type, within a specific
domain. For example, a continuous hole is bounded within a continuous
integer and has the type of a real value.

A combinator with no holes is filled.
